Secondary analysis of tables

### 2020-03-18 Analysis/06_Analysis_Tables.Rmd
Add correlation of slopes and CIs with network sizes

---
title: "Secondary analysis of tables"
# author: "Author's Name"
# date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
  html_document:
    theme: cerulean
    toc: yes
---

@@

```{r}
max_genes <- 200 # Maximum number of genes for a network to be included
min_genes <- 10  # Minimum number of genes for a network to be included
fileNameIn0  <- "../manuscript/Tables/supplementary_table_S3.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S3.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
# Rename some diseases
mtx0$Disease[mtx0$Disease == "Attention deficit hyperactivity disorder"] <- "ADHD"
mtx0$Disease[mtx0$Disease == "Inflammatory bowel disease"] <- "IBD"
mtx0$Disease[mtx0$Disease == "Systemic lupus erythematosus"] <- "SLE"
mtx0$Disease[mtx0$Disease == "Age-related macular degeneration"] <- "Macular degeneration"
mtx0$Disease[mtx0$Disease == "Lupus nephritis in systemic lupus erythematosus"] <- "Lupus nephritis in SLE"

@@

@@

```{r}
# Selected data for correlation
# Remove small/large networks
mtx0_cor <- mtx0[ mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, min, na.rm = TRUE) > min_genes &
                  mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, max, na.rm = TRUE) < max_genes, ]
# Remove size columns
mtx0_cor <- mtx0_cor %>% dplyr::select(contains("Coherence"), contains("Number"), contains("P value"), contains("Modularity"))
# Jitter STRING p-value a bit
set.seed(1)
mtx0_cor$`String P value` <- jitter(mtx0_cor$`String P value`, amount = 0.0001)
# Actual correlation
diff_cors <- cor(mtx0_cor, use = "pairwise.complete.obs")
# Average correlation with network size
diff_cors_selected <- diff_cors[grepl("Number", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation with network size: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of STRING and STRING filtered coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)) & grepl("String", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors)) & grepl("String", colnames(diff_cors))]
print(paste0("Average correlation of STRING coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation of coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences and p-value
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("P value", colnames(diff_cors))]
print(paste0("Average correlation of coherences and p-value: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))

# corrgram::corrgram(diff_cors, order = FALSE, upper.panel=panel.cor)
corrplot.mixed(diff_cors, lower = "number", lower.col = col3(100), upper = "circle", upper.col = col3(100), tl.cex = 1, tl.pos = "lt", tl.col = "black")
# Selected correlations
png(filename = "../manuscript/Figures/FigS1_corr_coherence.png", height = 2000, width = 2000, res = 300)
# corrgram::corrgram(diff_cors, order = FALSE, upper.panel=panel.cor, cex.labels = 4)
corrplot.mixed(diff_cors, lower = "number", lower.col = col3(100), upper = "circle", upper.col = col3(100), tl.cex = 1, tl.pos = "lt", tl.col = "black")
dev.off()
```

@@

>>>>

---
title: "Secondary analysis of tables"
# author: "Author's Name"
# date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
  html_document:
    theme: cerulean
    toc: yes
editor_options: 
  chunk_output_type: console
---

@@

```{r}
max_genes <- 200 # Maximum number of genes for a network to be included
min_genes <- 10  # Minimum number of genes for a network to be included
fileNameIn0  <- "../manuscript/Tables/supplementary_table_S3.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
fileNameIn1 <- "../manuscript/Tables/Confidence_Intervals.csv" # Confidence intervals, generated in 03_Normalized_Coherence 2020-03-17
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S3.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
# Rename some diseases
mtx0$Disease[mtx0$Disease == "Attention deficit hyperactivity disorder"] <- "ADHD"
mtx0$Disease[mtx0$Disease == "Inflammatory bowel disease"] <- "IBD"
mtx0$Disease[mtx0$Disease == "Systemic lupus erythematosus"] <- "SLE"
mtx0$Disease[mtx0$Disease == "Age-related macular degeneration"] <- "Macular degeneration"
mtx0$Disease[mtx0$Disease == "Lupus nephritis in systemic lupus erythematosus"] <- "Lupus nephritis in SLE"

@@

### Append confidence intervals

```{r}
# Should be done one time
mtx <- read_csv(fileNameIn1)
mtx0 <- left_join(mtx0, mtx, by = c("Disease", "Category"))
write_csv(mtx0, fileNameIn0)
```

@@

```{r}
# Add CI size
mtx0 <- mtx0 %>% mutate(`CI Biogrid`=`Biogrid Upper`-`Biogrid Lower`, `CI String`=`String Upper`-`String Lower`, `CI String Filt`=`String Filt Upper`-`String Filt Lower`)
# Selected data for correlation
# Remove small/large networks
mtx0_cor <- mtx0[ mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, min, na.rm = TRUE) > min_genes &
                  mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, max, na.rm = TRUE) < max_genes, ]
# Remove size columns
mtx0_cor <- mtx0_cor %>% dplyr::select(contains("Coherence"), contains("Number"), contains("P value"), contains("Modularity"), contains("Slope"), contains("CI"))
# Jitter STRING p-value a bit
set.seed(1)
mtx0_cor$`String P value` <- jitter(mtx0_cor$`String P value`, amount = 0.0001)
# Actual correlation
diff_cors <- cor(mtx0_cor, use = "pairwise.complete.obs")
# Average correlation with network size
diff_cors_selected <- diff_cors[grepl("Number", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation with network size: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of STRING and STRING filtered coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)) & grepl("String", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors)) & grepl("String", colnames(diff_cors))]
print(paste0("Average correlation of STRING coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation of coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences and p-value
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("P value", colnames(diff_cors))]
print(paste0("Average correlation of coherences and p-value: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of slopes and network sizes
diff_cors_selected <- diff_cors[grepl("Slope", rownames(diff_cors)), grepl("Number of genes", colnames(diff_cors))]
print(paste0("Average correlation of sloped and the number of genes: ", mean(diff_cors_selected)))
# Average correlation of CIs and network sizes
diff_cors_selected <- diff_cors[grepl("CI", rownames(diff_cors)), grepl("Number of genes", colnames(diff_cors))]
print(paste0("Average correlation of CIs and the number of genes: ", mean(diff_cors_selected)))

# corrgram::corrgram(diff_cors, order = FALSE, upper.panel=panel.cor)
corrplot.mixed(diff_cors, lower = "number", lower.col = col3(100), upper = "circle", upper.col = col3(100), tl.cex = 1, tl.pos = "lt", tl.col = "black")
# Selected correlations
png(filename = "../manuscript/Figures/FigS1_corr_coherence.png", height = 3000, width = 3000, res = 300)
# corrgram::corrgram(diff_cors, order = FALSE, upper.panel=panel.cor, cex.labels = 4)
corrplot.mixed(diff_cors, lower = "number", lower.col = col3(100), upper = "circle", upper.col = col3(100), tl.cex = 1, tl.pos = "lt", tl.col = "black")
dev.off()
```

@@

# Confidence Interval investigation

```{r eval=FALSE}
mtx_ci_dotplot <- function(category = "Intelligence", mtx_traits = mtx, databases = c("Biogrid", "String", "String.Filt")) {

  mtx_traits_selected <- mtx_traits[mtx_traits$Category == category, grepl(databases, colnames(mtx_traits), fixed = TRUE)]

  mtx_traits_selected_to_plot <- data.frame(Disease = rownames(mtx_traits_selected), 
                                            Slope = mtx_traits_selected[, paste0(databases, ".Slope")], 
                                            Lower = mtx_traits_selected[, paste0(databases, ".Lower")],
                                            Upper = mtx_traits_selected[, paste0(databases, ".Upper")])
  # Remove noninformative rows
  mtx_traits_selected_to_plot <- mtx_traits_selected_to_plot[complete.cases(mtx_traits_selected_to_plot), ]
  # Sort by decreasing level of slope
  mtx_traits_selected_to_plot$Disease <- factor(mtx_traits_selected_to_plot$Disease, levels = mtx_traits_selected_to_plot$Disease[order(mtx_traits_selected_to_plot$Slope)])

  p <- ggplot() +
    geom_point(data=mtx_traits_selected_to_plot, mapping=aes(x=Disease, y=Slope), size=4, shape=21, fill="white") +
    geom_errorbar(data=mtx_traits_selected_to_plot, mapping=aes(x=Disease, ymin=Lower, ymax=Upper), width=0.2, size=1, color="blue") +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab("Slope (unnormalized coherence") +
    # geom_text_repel(size = 4, colour = "black") +
    coord_flip() +
    # theme_cowplot(12) +
    theme(legend.position="none") +
    theme(axis.text = element_text(size = 12)) + 
    ggtitle(category)
}

```
